Gaussian mean estimation in simulated data sets

### 2020-06-16 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

In this next scenario, the data sets were simulated using the "Corner"
mean function and the "Doppler" variance function. These plots were
also used in Fig. 3 of the manuscript.

This plot shows the mean function as a black line, and the +/- 2
standard deviations as orange lines:

```{r corner-signal, fig.height=4, fig.width=6}
mu        <- cor.fn(t,"mean") 
sigma.ini <- sqrt(doppler.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
```

@@

```{r corner-signal-with-estimates, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- cor.fn(t,"mean") 
sigma.ini <- sqrt(doppler.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
x.sim  <- rnorm(1024,mu,sd.fn)
mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                      filter.number = 8)
par(cex.axis = 1)
plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```

>>>>

In this next scenario, the data sets were simulated using the "Corner"
mean function and the "Doppler" variance function. These plots were
also used in Figure 3 of the manuscript.

```{r corner-signal, fig.height=4, fig.width=6}
t         <- (1:1024)/1024
mu        <- cor.fn(t,"mean") 
sigma.ini <- sqrt(doppler.fn(t,"var"))
sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
x.sim     <- rnorm(1024,mu,sd.fn)
plot(mu,type = "l",col = "darkorange",ylim = c(-0.05,1),
     xlab = "position",ylab = "",lwd = 1.75,xaxp = c(0,1024,4),
     yaxp = c(0,1,4))
lines(mu + 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
lines(mu - 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
points(x.sim,cex = 0.7,pch = 1,col = "black")
```

@@

```{r corner-signal-with-estimates, fig.height=4, fig.width=6}
mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                      filter.number = 8)
par(cex.axis = 1)
plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```
